---
title: "Salmon Temperature Model"
author: "Austin, Alexander, and Savannah"
date: "May 9, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#Notes
-Baseline data: use average monthly data (streamflow and temperature) for the average of 5 water years from 2014-2018 --> this is the highest generality/aggregation that can avoid the variability of flow and temperature data on smaller times steps, but that is still relevant to salmon migration (monthly data captures seasonal migration)
Example:
M Q T
1 3 18
2 5 17
3 9 14
4 7 16
......





```{r}
#Load packages
library(tidyverse)
library(deSolve)

```

#Baseline Model Run
```{r}
#Load Dworshack Reservoir streamflow and temperature data
dworshack <- read_csv()

#Wrangle data

#Load the South Clear Water River streamflow and temperature data
s_clear_water <- read_csv()

#Wrangle data

```

```{r}
#Mixing of Dworshack and South Clear Water River
source("../R/mix.R")
main_seg_1 <- mix()

```

```{r}
#Load Middle Snake River streamflow and temperature data
mid_snake <- read_csv()

#Wrangle data

```

```{r}
#Mixing of Main River Segment 1 with Middle Snake River
source("..R/mix.R")
main_seg_2 <- mix()

```

```{r}
#Load air temperature data near Lower Granite Dam
air_temp <- read_csv()

#Wrangle data

```

```{r}
#Model conduction heat gain of reservoir due to air temperature
source("..R/air_conduction.R")
lower_granite <- ode(y = , times = , func = air_conduction, parms = )

```

```{r}
#Calculate Electrical Hydropower Generation
source("..R/power_gen.R")
hydropower <- power_gen()
```

```{r}
#Visualize Results

```


#Sensitivity Analysis
##Scenario 1: 
 
##Scenario 2:

##Scenario 3:

##Scenario 4:
 