---
title: "Salmon Temperature Model"
author: "Austin, Alexander, and Savannah"
date: "May 9, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



There are 5 general steps to this model:

1. Cold water is released from Dworshack dam (North Fork of the Clearwater River) and generates power

2. The cold water released from Dworshack dam (the North Fork of the Clearwater River) mixes with the warm water of the mainstem of the Clearwater River

3. The mixed Clearwater River mixes with the warm water of the Middle Fork of the Snake River

4. The mixed Snake River water enters the forebay of Lower Granite Dam where it is warmed by solar radiation

5. Water is released from Lower Granite Dam, which also generates power


Model is first completed using input data from 2018. This shows us the relative contribution of temperature sources in the system.

Later the individual parameters are changed to understand how changes to the system may impact temperature:
  - increased release of water from dworshack August-October
  - temperature decrease on the Snake River (decrease by 2 degrees)
  - if air temp increase by 2 degrees C, how much does that change warming in the reservoir

# Step 1: Cold Water is released from Dworshack Dam and generates power

##Load libraries and data
```{r}

library(tidyverse)
library(readr)

```

```{r}

#load elevation data
dworshack_elv <- read_csv("../Data/dworshack_elv.csv") 

#load flow data
dworshack_flow <- read_csv("../Data/dworshack_flow.csv")

```


## Calculate power generation model inputs

### Calculate head and convert from ft to m
head (ft) = forebay elevation (ft) - tailwater elevation (ft)

```{r}

# create new column that calculates head and remove NAs
dworshack_head <- dworshack_elv %>% 
  mutate(head = (forebay_elv - tailwater_elv)) %>% 
  select(date, head) %>% 
  na.omit() 

# convert head from ft to m
dworshack_head <- mutate(dworshack_head, head_m = dworshack_head$head*0.305)

```

### Calculate flow for power generation and convert to m3/s 

This could be an input parameter (observed data exists), but then there would be no change in power generation when outflow values are changed. 

flow availabile for power generation (kcfs) = total outflow (kcfs) - spill (kcfs) - losses(kcfs)

```{r}

#create column with flows avaialble for power generation assuming 5% loss

perc_loss = 0.05 #start with 5% loss

power_flow <- dworshack_flow %>% 
  mutate(calc_power_flow = (total_outflow - spill_flow)) %>% 
  mutate(losses = calc_power_flow*perc_loss) %>% 
  mutate(power_flow_wlosses = calc_power_flow - losses) 

#convert kcfs to m3/s 
power_flow <- power_flow %>% 
  select(date, total_outflow, spill_flow, power_flow_wlosses) %>% 
  mutate(total_outflow_m3s = (total_outflow * 28.32)) %>% 
  mutate(spill_flow_m3s = spill_flow * 28.32) %>% 
  mutate(power_flow_wlosses_m3s = power_flow_wlosses * 28.32)


```


### Merge final historic data inputs for power gneration at Dworshack into single data frame

```{r}

# keep flow inputs with correct units
flow_inputs <- power_flow %>% 
  select(date, total_outflow_m3s, spill_flow_m3s, power_flow_wlosses_m3s) 

head_inputs <- dworshack_head %>% 
  select(date, head_m)
  
historic_inputs <- merge(flow_inputs, head_inputs)
historic_inputs$date <- as.Date(historic_inputs$date, "%m/%d/%Y")

```


## Run power generation model

```{r}

source("../R/dshack_powergen.R")

test_data <- historic_inputs %>% 
  select(date, power_flow_wlosses_m3s, head_m) %>% 
  mutate(date = ymd(date)) %>% 
  mutate_at(vars(date), funs(year, month, day)) %>% 
  filter(year == 2018)

reservoir_model_res= as.data.frame(matrix(nrow=365, ncol=4))
colnames(reservoir_model_res)=c("date", "head","flowrate","power")

reservoir_model_res$date = test_data$date
reservoir_model_res$head = test_data$head_m
reservoir_model_res$flowrate = test_data$power_flow_wlosses_m3s


reservoir_model_res$power = mapply(FUN=max_power, head =reservoir_model_res$head, flow=reservoir_model_res$flowrate)


#umultiply final result by 2.5. Theere are 3 generators/turbines in the dam. They are not always operational and not always at full capactiy. The value of 2.5 provides a good match to observed data.  
reservoir_model_res <- mutate(reservoir_model_res, power_MW = ((power/100000)*2.5))


```


# Step 2: Water from Dworshack dam (the North Fork of the Clearwater River) mixes with the mainstem of the Clearwater River
